### 2021-02-24 paper.Rmd
notes to self

<!-- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
-->
- Alternatives (Stuart)

>>>>

<!-- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
(picture of the cluster data from Stuart's thesis)
-->
- Alternatives (Stuart)

(parallel coordinates, sploms, what tours are not)
